%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4,10pt]{article}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage{parskip} 	
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[a4, margin=0.9in]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{supertabular}
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}
\usepackage[unicode, draft=false]{hyperref}
\usepackage{fontawesome5}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{8pt}

\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------
\begin{tabularx}{\linewidth}{@{} l X @{}}
\Huge {SWASTIK SHARMA} & \hfill 
\end{tabularx}
% \hrule % Horizontal rule

\begin{flushleft}
% Using \href with Font Awesome icons
\href{https://www.swastiksharma.in}{\raisebox{-0.05\height}{\faGlobe} swastiksharma.in} $|$ 
\href{mailto:swastkk@gmail.com}{\raisebox{-0.05\height}{\faEnvelope} swastkk@gmail.com} $|$ 
\href{https://github.com/swastkk}{\raisebox{-0.05\height}{\faGithub} swastkk} $|$ 
\href{https://linkedin.com/in/swastkk}{\raisebox{-0.05\height}{\faLinkedin} swastkk} $|$ 
\href{tel:+919805279184}{\raisebox{-0.05\height}{\faMobile} +91 9805279184}

\end{flushleft}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}
\textbf{Indian Institute of Technology}  \hfill {Mandi, India}  \\
    \textit{{Minor in CSE \&\ Next Gen technologies Program, CCE - IIT Mandi} \hfill {October 2024 - present}}
    
 \textbf{National Institute of Technology}  \hfill {Hamirpur, India}  \\
    \textit{{Bachelor of Technology - Electrical Engineering; CGPA: 7.99/10} \hfill {December 2021 - present}}
    \begin{itemize}[leftmargin=*,label=$\diamond$]
        \item \small \textbf{Relevant Coursework:} \textit{Data Structures and Algorithms (DSA), Database Management Systems (DBMS), Object Oriented Programming (OOPs),  Computer Networks}
         \item \small \textbf{Minors:} \textit{Engineering Economics \& Accountancy, Industrial Psychology, Indian Business Environment}
    \end{itemize}
%     \item \textbf{Govt Senior Secondary School} \hfill {Daulatpur Chowk, India} \\
%     \textit{XII HP Board; Percentage: 90\%} \hfill \textit{April 2021}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{itemize}[leftmargin=*]
    \item \textbf{Languages:} Python, GO, Rust, C, C++, HTML, CSS, JavaScript, SQL
    \item \textbf{Frameworks:} Tauri, ReactJS, NextJS, Django, Flask, FastAPI, Django-REST Framework, Svelte, Hugo
    \item \textbf{Tools:} Git/GitHub, GitHub Actions, GitLab, Postman, PostgreSQL, Jinja, LaTeX
    \item \textbf{Platforms:} Linux, Web, Windows, Raspberry Pi, Arduino
    \item \textbf{Soft Skills:} Brainstorming, Teamwork, Leadership, Communication
\end{itemize}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Work Experience}
\begin{itemize}[leftmargin=*]

\item \textbf{Valiant Fintech Pvt. Ltd. | BeyondIRR}  \hfill {Mumbai, Maharashtra} \\
\textit{SDE Intern(Hybrid)}  \hfill \textit{Sept 2024 - present}
\begin{itemize}[label=$\diamond$]
    \item Developed and optimized 5+ production-level Wealthtech platform web applications using Django/DRF and Flask, improving performance by 30\% on an average that are deployed over custom cloud environment.
    \item Implemented and ensured seamless Azure AD integrations for authentication, supporting 5+ enterprises with 100\% uptime for authorization systems.
    \item Collaborated with 10+ clients as part of a SaaS-based environment, delivering tailored solutions to meet specific requirements, reducing deployment errors by 20\%. Also streamed Files with S3 pre-signed URLs with implementing custom cloudfront key verification logic.
\end{itemize}

\item \textbf{Shucon Solutions Private Limited}  \hfill {Remote} \\
\textit{Django Developer(Part-Time)}  \hfill \textit{Dec 2024 - Mar 2025}
\begin{itemize}[label=$\diamond$]
    \item Created scalable Django REST APIs from scratch and successfully released version 2, ensuring stability and robustness in production.  
    \item Designed the system architecture for a Hospital Management System, optimizing patient record management, billing, and appointment scheduling.  
\end{itemize}

\item \textbf{Google Summer of Code '24 - AboutCode}  \hfill {Remote} \\
\textit{Open Source Developer (Full time)}  \hfill \textit{May 2024 - August 2024}
\begin{itemize}[label=$\diamond$]
    \item  Increased scanning precision by \textbf{40\%} through detailed package/file-level summaries \& improving accuracy for SCA (Software Composition Analysis).
    \item Improved package assembly detection to ensure accurate and reliable results, with over 20+ tests added to validate the process across various ecosystems.

\end{itemize}

% \item \textbf {Athena Consulting} \hfill Remote \\[3.75pt]
% \textit{Backend Developer(Internship)} \hfill \textit{June 2023 - September 2023}
% \begin{itemize}[label=$\diamond$]
%     \item \small Directed the integration of Concordium blockchain technology via Concordium Rust SDK and Optimized the Rust Tauri Desktop Application's performance.
\end{itemize}
% \end{itemize}
%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------
\section{Projects}
% \begin{itemize}[leftmargin=*]
% \item \textbf{WALLPAPE-RS} $|$ Rust, Tauri, ReactJS  \hfill \href{https://github.com/swastkk/wallpape-rs}{Link}
% {\small
% \begin{itemize}[label=$\diamond$,itemsep=0pt]
%     \item Crafted a cross-platform desktop app using Rust \& Tauri, enabling seamless wallpaper customization with a click.
%     \item Achieved a lightning-fast speed of wallpaper change, with transitions as swift as \textbf{0.5 seconds} per change. This enhancement resulted in a \textbf{25\% increase} in user engagement metrics and a \textbf{15\% decrease} in user-reported issues related to customization.
% \end{itemize}
% }
\begin{itemize}[leftmargin=*]
\item \textbf{Package Summary} $|$ Python, Packaging, Package Ecosystems  \hfill \href{https://github.com/aboutcode-org/scancode-toolkit}{Link}
\begin{itemize}[label=$\diamond$,itemsep=0pt]
    \item Computed a package-level summary that includes the calculation of License Clarity Score and the population of various package attributes such as copyrights, holders, notice texts, and other license expressions.
    \item Architected and refactored the code to ensure that various package ecosystems like npm, Python (whl), Rubygems, and many more can be handled properly.
    \item Authored robust tests for 20+ package ecosystems to ensure reliability and accuracy.
\end{itemize}

\item \textbf{Prodyogiki'24} $|$ NextJS, Django, DRF, Docker, PostgreSQL \hfill \href{https://github.com/istenith/prody-frontend}{Frontend} $|$ \href{https://github.com/istenith/prody-backend}{Backend}

\begin{itemize}[label=$\diamond$]
    \item Developed a scalable NextJS and Django Full Stack Website for College Fest \textbf{Prodyogiki'24} at NITH.
    \item Accommodated \textbf{1000+ individual participants} and \textbf{150+ team} members across 10 events \& increased user engagement and streamlined organization processes.
\end{itemize}

\item \textbf{Application Portal} $|$ Python, Django, Docker, PostgreSQL, Celery  \hfill \href{https://github.com/istenith/join.istenith.com}{Link}

\begin{itemize}[label=$\diamond$]
    \item Utilized Django backend tools for Application Portal(similar to Google Forms) and reduced field customization time by \textbf{50\%}.
    \item Served over 500 college students, utilized for over \textbf{6 interview cycles} \& Achieved a \textbf{30\% reduction} in administrative overhead and established data security.
\end{itemize}

\end{itemize}
%----------------------------------------------------------------------------------------
%	AWARDS
%----------------------------------------------------------------------------------------
\section{Honors and Awards}
\begin{enumerate}[leftmargin=*, itemsep=0em]
    \item Google Summer of Code 2024 Scholar
    \item Summer of Bitcoin 2025 Workshop Mentee
    \item Second Runner at \textbf{ASCENSIO}, Open Exhibition conducted under Annual Technical Fest of NIT Hamirpur -April 2023.
    % \item Finalist in \textbf{Hack.AI} at TECHFEST IIT Bombay 2023, led a team to develop solutions, resulting in a 30\% efficiency boost, ranking top 50 nationwide among \textbf{300+ teams}.
    \item Orchestrated a groundbreaking project at TECHFEST IIT BOMBAY, December 2023, placing as a finalist in \textbf{Hack.AI}; leveraged cutting-edge AI techniques to enhance user experience, boosting app engagement by \textbf{40\%}.
    \item Ranked in the top 10 nationwide teams at Hackathon \textbf{Hack it out}, at TECHNEX, IIT-BHU -March 2023.
    \item 2nd Runner-Up at Electrothon 5.0, NIT Hamirpur, outperforming \textbf{70+} teams \& secured MLH Fellowship Interview.
\end{enumerate}


%----------------------------------------------------------------------------------------
%	EXTRA CURRICULAR AND POSITION OF RESPONSIBILITY
%----------------------------------------------------------------------------------------
\section{Extra Curricular $|$ \normalsize{Position of Responsibility}}

\begin{itemize}[leftmargin=*, itemsep=0em]
    \item \textbf {Joint Secretary at Indian Society for Technical Education,} \textit{Student's Chapter} \hfill Hamirpur, India\\
    \textit {Organised many events like Hult Prize, Prodyogiki with \textbf{1500+} participants. \hfill Jan 2022 - May 2025}
    
    \item \textbf {Training \& Placement Representative, NIT Hamirpur} \hfill Hamirpur, India\\
    \textit{ Managed relations between the Placement Cell, 50+ recruiters, and \textbf{850+} students. \hfill April 2024 - May 2025}
    
    \item \textbf{Member at GNU/Linux User's Group, NITH} \hfill Hamirpur, India\\
    \textit Organised Open Source Month'23 with more than \textbf{150+} new contributors. \hfill January 2022 - May 2025
\end{itemize}


\end{document}
 
